Clustering SCPCL000822 and SCPCL000824

### 2024-08-01 analyses/cell-type-ewings/exploratory_analysis/05-cluster-exploration.Rmd
render notebook

# define output files
cluster_results_dir <- file.path(module_base, "results", "clustering", sample_ids)
cluster_results_dir |>
  purrr::map(fs::dir_create)

@@

```{r}
# perform clustering across k = 5-40 with increments of 5
all_cluster_results <- sce_list |>
  purrr::map(get_clusters) |>
  dplyr::bind_rows(.id = "library_id")
```

@@

# plot stability across all values of k
ggplot(stability_df, aes(x = k_value, y = ari)) +
  geom_point() +
  facet_grid(rows = vars(library_id)) +
  title("Cluster stability")
```

>>>>

# define output files
cluster_results_dir <- file.path(module_base, "results", "clustering", sample_ids)
cluster_results_dir |>
  purrr::walk(fs::dir_create)

@@

```{r}
# perform clustering across k = 5-40 with increments of 5
all_cluster_results <- sce_list |>
  purrr::map(cluster_sweep) |>
  dplyr::bind_rows(.id = "library_id")
```

@@

# plot stability across all values of k
ggplot(stability_df, aes(x = k_value, y = ari)) +
  geom_point() +
  facet_grid(rows = vars(library_id)) +
  labs(title = "Cluster stability")
```
